### 2015-12-04 paper.tex
Add strut covers drawing; resolves #32

>>>>

For investigating the effects of support strut drag losses, a set of cylindrical
strut covers was designed to slip over the blades. Endcaps were also fabricated
to allow the high drag strut cover configuration to be operated without blades.
A drawing of the strut covers is shown in Fig.~\ref{fig:covers}.

\begin{figure}[h]
    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

    \caption{{\bf Strut Covers.} A drawing of the high drag strut cover
        configuration with and without blades.}

    \label{fig:covers}
\end{figure}
